\section{Setup and run}
\subsection{Etherless-cli}
\subsubsection{Requirements}
To run correctly this component you need to install:
\begin{itemize}
    \item \textbf{Node.js}: to install it, you can refer to the official web page nodejs.org we recommend the LTS version;
    \item \textbf{npm}: npm is the package manager that comes with Node.Js;
    \item \textbf{TypeScript}: to install TypeScript you need to run npm install typescript -g, the minimum version required is the 3.6.5;
    \item \textbf{ts-node}: to install ts-node you need to run npm install ts-node -g, this operation will install globally the command ts-node;
    \item \textbf{mocha} \textit{optional, needed only in test environment}: to install mocha you need to run npm install mocha -g, this operation will install globally the command mocha;
\end{itemize}

\subsubsection{Setup}
To install Etherless-cli is sufficient to run npm install --dotenv-extended.
Before to start using the software you need to register an Ethereum account or login with an already existing one, after the that you need to add funds to your wallet.
You can do that by importing the new account in MetaMask.
\subsubsection{Run}
To run this program from the command line interface positioning on the main program folder
and type ts-node . <<command>> where <<command>> is the command that you want to run.
\subsection{Etherless-smart}
\subsubsection{Requirements}
To run correctly this component you need to install:
\begin{itemize}
    \item \textbf{Truffle}: to install Truffle you need to run npm install Truffle -g, the minimum version required is the 3.6.5;
    \item \textbf{Ganache}: Ganache is available 
    \item \textbf{TypeScript}: to install TypeScript you need to run npm with elevate privileges and run npm install typescript -g, the minimun version required is the 3.6.5;
    \item \textbf{ts-node}: to install ts-node you need to run npm with elevate privileges and run npm install ts-node -g, this operation will install globally the command ts-node;
    \item \textbf{mocha} \textit{optional, needed only in test environment}: to install mocha you need to run npm with elevate privileges and run npm install mocha -g, this operation will install globally the command mocha;
\end{itemize}

\subsubsection{Setup}
Before beginning the installation process you need three different keys: an Etherscan API key, and Infura API key and a private key from your Ethereum account.
After obtain the credential you need to edit the truffle-config.js file replacing the fields at the top with your own.
Now you are ready to install Etherless-smart in a production like environment, running the following commands from the component folder will install your smart application in the chosen network.

\begin{itemize}
    \item npm install --dotenv-extended
    \item truffle build
    \item truffle deploy --network test
    \item truffle run verify EtherlessSmart --network test
\end{itemize}
After the deploy is a good practice to save the contract address somewhere safe, that will be needed when you want to retrieve the contract later.
\subsubsection{Run}
After the deploy your contract will be always available and runnable through a web3 application like Remix with MetaMask injection.
\subsection{Etherless-Server}
\subsubsection{Setup}
Before beginning the installation process you need to install the aws credential on your machine, or you can register on Serverless framework website that will handle the deploy and permission management for you.
If you completed the setup correctly running serverless deploy will upload the application to you lambda account and will be executable from the web.
\subsubsection{Run}
If you completed the setup correctly running serverless deploy will upload the application to you lambda account and will be executable from the web.
