\section{Used technologies}

\subsection{Languages}
\subsubsection{Typescript v3.6.5}
TypeScript is an open-source language which builds on JavaScript, one of the world’s most used tools, by adding static type definitions.\\
Types provide a way to describe the shape of an object, providing better documentation, and allowing TypeScript to validate that your code is working correctly.

\subsubsection{Solidity v0.5.12}
Solidity is an object-oriented, high-level language for implementing smart contracts.
Smart contracts are programs which govern the behavior of accounts within the Ethereum state.

\subsection{Utilities}

\subsubsection{Npm v6.14.4}
npm is the world’s largest software registry. Open source developers from every continent use npm to share and borrow packages, and many organizations use npm to manage private development as well.\\
npm is committed to making JavaScript development elegant, productive, and safe. The free npm Registry has become the center of JavaScript code sharing, and with more than one million packages, the largest software registry in the world. 

\subsubsection{Node.js v12.6-LTS}
Node.js is an open source, cross-platform runtime environment for developing server-side and networking applications. 
Node.js applications are written in JavaScript, and can be run within the Node.js runtime on OS X, Microsoft Windows, and Linux.
Node.js also provides a rich library of various JavaScript modules which simplifies the development of web applications using Node.js to a great extent.

\subsubsection{TS-Node v8.8.1}
TS-Node is a wrapper for Node.js that lets the user run TypeScript application without compiling before the execution.

\subsubsection{Visual Studio Code}
Visual Studio Code is a configurable text editor with an extensible library of extensions that can make it a real IDE for many programming languages.

\subsubsection{AWS Lambda}
AWS Lambda is an Amazon’s service that lets you run any web application without worry about managing the server and paying only for the resources used only when the application is in use.

\subsubsection{AWS Elastic Beanstalk}
AWS Elastic Beanstalk is an Amazon’s service that distributes an application between many servers and checks the application’s health and scales the resources on the fly meeting the needs on-demand.

\subsubsection{ESLint}
ESLint is a JavaScript configurable linter that helps developers to follow a code style guidelines chosen and highlights common problems and bad practices.

\subsubsection{Truffle}
Truffle is a development environment for developing a Solidity application that provides tools for building the applications and for the deploy on any Ethereum network.

\subsubsection{Ganache-cli/Ganache}
Ganache is a local Ethereum network used for testing Solidity applications.

\subsubsection{GitHub}
GitHub is a git service that provides a remote repository that lets the users share the code and manage the flow of increments and changes.

\subsubsection{GitHub Actions}
GitHub Actions is a GitHub's service that runs automation script.
We used this service to run our unit test scripts, code coverage, cyclomatic complexity, and to calculate the comments and code line ratio.

\subsubsection{nyc}
nyc is a CLI interface to run Istanbul application that returns the code coverage.

\subsubsection{Istanbul}
Istanbul is a code coverage application that check which lines of code the unit test execute when running.

\subsubsection{CLOC}
CLOC counts blank lines, comment lines, and physical lines of source code in many programming languages. Given two versions of a code base, CLOC can compute differences in blank, comment, and source lines.

\subsubsection{Code Metrics CLI}
Code Metrics CLI is a utility that calculates the cyclomatic complexity in any JavaScript or TypeScript program.


\subsection{Libraries}

\subsubsection{Axios v0.19.2}
Axios is JavaScript library that provides HTTP and HTTPS functionalities letting the user perform all the HTTP requests.

\subsection{AWS SDK}
AWS sdk is a JavaScript library that provides a simple way to interact with the Amazon’s web services

\subsubsection{Commander}
Commander si a JavaScript library that lets the user create a CLI applications effortlessly.

\subsubsection{web3}
Wb3js is a JavaScript library commonly used to make requests to a Ethereum network.

\subsubsection{ts-mockito v2.5.0}
ts-mockito is mocking library specifically built for TypeScript used for unit testing that lets the user create a mock of any object defining the behavior of every methods.

\subsubsection{mocha v7.1.1}
Mocha is a unit test library that create the testing environment for JavaScript and TypeScript applications.

\subsubsection{chai v4.2.0}
Chai is an assertion and use case library that check the application's behavior on a unit test environment.

\subsubsection{web3-fake-provider v0.1.0}
Web3-fake-provider is a mocking library that mocks the behavior of a real Ethereum service provider.

