\section{Glossary}
\textbf{B}
\begin{itemize}
	\item \textbf{Blockchain}: A system in which a record of transactions made in bitcoin or another cryptocurrency are maintained across several computers that are linked in a peer-to-peer network.
\end{itemize}
\textbf{C}
\begin{itemize}
	\item \textbf{Cli}: A command line interface is a type user interface characterized by a textual interaction between the user and the computer. The user gives text input commands through an alphanumeric keyboard and receives text answers in output from the computer via display.
	\item \textbf{Cloud}: Indicates a paradigm for the provision of services offered on demand by a supplier to a customer
	final through the Internet, starting from a set of pre-existing, configurable and
	available remotely in the form of distributed architecture.
\end{itemize}
\textbf{E}
\begin{itemize}
	\item \textbf{Ethereum}: Ethereum is an open software platform based on blockchain\glo technology that enables developers to build and deploy decentralized applications.
\end{itemize}
\textbf{M}
\begin{itemize}
	\item \textbf{MetaMask}: MetaMask is a Plug-in available for Chrome, Firefox, Opera and Brave that allows you to interact with the Ethereum network without hosting a node and create multiple digital wallets. It is required to use in Soldino.
\end{itemize}
\textbf{N}
\begin{itemize}
	\item \textbf{Node.js}: Node.js is a JavaScript framework for building scalable web applications.
\end{itemize}
\textbf{P}
\begin{itemize}
	\item \textbf{Private-key}: In a blockchain\glo the private key is a key that guarantees ownership of the funds associated with
	a certain address.
\end{itemize}
\textbf{S}
\begin{itemize}
	\item \textbf{Serverless}: Adjective used to describe a software architecture that does not manage any server.
\end{itemize}
\textbf{T}
\begin{itemize}
	\item \textbf{TypeScript}: TypeScript is an open-source programming language developed and maintained by Microsoft. It is a strict syntactical superset of JavaScript, and adds optional static typing to the language. TypeScript is designed for development of large applications and transcompiles to JavaScript.
\end{itemize}
