\section{Introduction}
This document is the user manual for Etherless, a project developed by Tenners based on \textit{Ethereum\glo} infrastructure.

\subsection{Purpose of the document}
The purpose of this document is to illustrate the features present in the Etherless application and explain their use.

\subsection{What is Etherless}
Etherless is a Cloud Application Platform which allows developers to deploy Javascript functions in the cloud and let pay final users for their execution (e.g. Computation-as-a-service, CaaS), by leveraging the \textit{Ethereum\glos}'s smart contract technology.\\
The platform is managed and maintained by the Administrators. 
Developers can deploy Javascript functions into the platform. Users, finally, can run those functions provided they pay the fees set by the developers. Such fees are partially held by the platform itself as a compensation for the expenditure of the actual function execution.\\
Etherless is built integrating the two aforementioned technologies, \textit{Ethereum\glo} and Serverless. \textit{Ethereum\glo} will be responsible for the payments and triggering the invocation of the functions. Serverless will be responsible for the execution of the functions. A command line interface (CLI) will be the bridge for actual usage for developers and users. The (virtual) communication between \textit{Ethereum\glo} and Serverless will be achieved instead by listening and emitting \textit{Ethereum\glo} events. 


\subsection{Glossary}
To make clear any terms that could cause ambiguity, a glossary has been included in the appendix containing all the terms necessary for the understanding of this document. Words with a reference to the glossary will always be indicated by a subscript G. Example: word\glo If a word belonging to the Glossary is present in the title of a section or subsection, this is not indicated by the subscript G.
