\section{Troubleshooting}
While using the application, error messages may appear, if the user does not enter correct data or does not follow the correct procedures.
\subsection{Installation errors}
\begin{itemize}
	\item \textbf{Unable to install dependences:} make sure to update npm references so ensure the package manager is aware of all latest available packages\\\\ \centerline{\code{npm update}}
	\item \textbf{EACCESS error:} the package manager is unable to install global commands; please refer to the following page to gather further information on this issue\\\\\centerline{\code{https://docs.npmjs.com/resolving-eacces-permissions-errors-when-installing-packages-globally}}
\end{itemize}
\subsection{Common errors}
\begin{itemize}
	\item \textbf{Internet error:} no internet connection;
%	\item Given too many parameters;
	\item \textbf{Key derivation failed - possibly wrong password:} incorrect password;
	\item \textbf{Command not found error:} given command does not match command syntax;
	\item \textbf{Missing required argument};
\end{itemize}
\subsection{Logout errors}
\begin{itemize}
	\item \textbf{Already logged out.}
\end{itemize}
\subsection{Login errors}
\begin{itemize}
	\item \textbf{Private key must have 66 characters long: check the presence of the prefix 0x;}
	\item \textbf{Already logged in.}
\end{itemize}
\subsection{Signup errors}
\begin{itemize}
	\item \textbf{Already logged in.}
\end{itemize}
\subsection{Find errors}
\begin{itemize}
	\item \textbf{Function not found:} function doesn't exist.
\end{itemize}
\subsection{Create errors}
\begin{itemize}
	\item \textbf{Resource not available:} function already exists on Etherless;
	\item \textbf{Description too long:} description is longer than 50 characters;
	\item \textbf{No existing path}: file doesn't exist.
\end{itemize}
\subsection{Update errors}
\begin{itemize}
	\item \textbf{No existing path}: file doesn't exist;
	\item \textbf{Resource not available:} function name does not exists on Etherless or you're not the function owner.
\end{itemize}
\subsection{Delete errors}
\begin{itemize}
 	\item \textbf{Resource not available:} function name does not exists on Etherless or you're not the function owner.
\end{itemize}
\subsection{Run errors}
\begin{itemize}
	\item \textbf{Returned error: }insufficient funds for gas * price + value;
	\item \textbf{Resource not available:} function name does not exists on Etherless.
\end{itemize}
\subsection{Set errors}
\begin{itemize}
	\item \textbf{Invalid property. Only cost, description and prototype can be updated};
	\item \textbf{Resource not available:} function name does not exists on Etherless or you're not the function owner.
\end{itemize}


